Outline paper - Multiple imputation for statistical disclosure control: Creating synthetic datasets with *mice*

### 2020-08-25 mice_synthesizing/paper.Rmd
Small update paper.

Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@foster_open_science_2017; @walport_brest_sharing_2011]. HIER EEN VOORBEELD Additionally, the fact that public funds are used for data collection results in increased demands for the collected data. Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality. Simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009]. Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011]. However, these methods may distort relationships between variables, reducing the data quality drastically.

>>>>

Open science, including open data, has been marked as the future of science [@gewin_data_2016], and the advantages of publicly available research data are numerous [@molloy_open_2011; @walport_brest_sharing_2011]. As collecting research data requires an enormous investment both in terms of time and monetary resources, openly accessible research data bears the potential of increasing the scientific returns. Additionally, the fact that public funds are used for data collection results in increased demands for the collected data. Nevertheless, the possibilities to share research data directly are often very limited due to restrictions with regard to privacy and confidentiality. Simply anonimizing the data is not enough to fulfil these requirements [@ohm_broken_2009]. Over the years, several other techniques have been used to increase the confidentiality of the data, such as categorizing continuous variables, top coding values above a certain threshold or adding random noise [@drechsler_synthetic_2011]. However, these methods may distort relationships between variables, reducing the data quality drastically.
